\thetitle

### 2020-07-01 writing/introduction.tex
challenges first

Next, the paper provide an overview of the blame assignment strategies as found in
existing gradually typed language implementation (see section~\ref{sec:landscape})
and the challenges of developing a systematic evaluation method
(section~\ref{sec:challengs}).

>>>>

Next, the paper describes the challenges of developing an evaluation method
(section~\ref{sec:challengs}), which may explain why the question has been neglected
for such a long time. This description is followed by some background material on the
existing blame assignment strategies (see section~\ref{sec:landscape}).
